%-------------------------
% Resume in Latex
% Author : Leonard Kiyoshi Bogdonoff
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://rememberlenny.com/}{\Large Leonard Kiyoshi Bogdonoff}} & Email : \href{mailto:rememberlenny@gmail.com}{rememberlenny@gmail.com}\\
  \href{http://rememberlenny.com/}{http://www.rememberlenny.com} & Mobile : +1-949-322-8496 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Policygenius}{New York, NY}
      {Senior software engineer}{May 2020 - Present}

    \resumeSubheading
      {Google - Google Fonts - Material design}{New York, NY}
      {UX engineer}{Oct 2018 - May 2020}
      \resumeItemListStart
        \resumeItem{Variable fonts UX research}
          {Proactively explored complicated "variable fonts" concepts and engineered ideal solutions for Google Fonts users.}
        \resumeItem{Fonts search and filtering UI launch}
          {Worked on a skillset diverse team as the frontend engineer, and built out prototypes for research, while continually rolling out production releases. }
        \resumeItem{10 year anniversary redesign}
          {To celebrate, Google Fonts launched a new variable fonts API, and migrated and redesigned the entirety of Google Fonts.}
      \resumeItemListEnd

    \resumeSubheading
      {Comet.ml}{New York, NY}
      {Senior frontend engineer}{Feb 2018 - Oct 2018}
      \resumeItemListStart
        \resumeItem{App rewrite}
          {Rewrote an agency-built MVP using React and Redux.}
        \resumeItem{Dashboard builder UI}
          {Conceptualized and led development around major UI features that evolved into the application's main dashboard.}
        \resumeItem{Frontend design system}
          {Established unit/end-to-end testing practices, a design system for frontend components using Storybook.js, and standardized CSS patterns using SMACSS.}
      \resumeItemListEnd

    \resumeSubheading
      {18f.gsa.gov}{Washington, DC}
      {Innovation specialist - Senior software engineer}{Jan 2016 and Jan 2018}
      \resumeItemListStart
        \resumeItem{regulations.atf.gov}
          {Built templates for Next.js application that makes federal regulation easier to find, read and understand.}
        \resumeItem{cloud.gov}
          {Led feature development for user creation and team management workflow.}
        \resumeItem{seedfund.nsf.gov}
          {Prototyped eight Angular websites for rapid user testing.}
        \resumeItem{Communicart}
          {Engineering lead for a Ruby-on-rails accounting tool that allowed users to track expenses and approvals using email.}
      \resumeItemListEnd

    \resumeSubheading
      {Conde Nast}{New York, NY}
      {Senior software engineer}{Sep 2013 - Jan 2016}
      \resumeItemListStart
        \resumeItem{newyorker.com}
          {Contributed on a team of six engineers to re-platform the newyorker.com, build content distribution feeds, and various product templates.}
        \resumeItem{bonappetit.com}
          {Led engineering on a team of two to re-platform the bonappetit.com website.}
        \resumeItem{wmagazine.com}
          {Built a Backbone.js application for browsing content for W Magazine.}
      \resumeItemListEnd


    \resumeSubheading
      {Converse APAC}{Shanghai, China}
      {Technical project manager}{Winter 2012}


    \resumeSubheading
      {iTalki}{Shanghai, China}
      {Frontend web developer}{Aug 2012 - Dec 2012}


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Public art}
      {6+ year project that received multiple high-profile grants to track millions of geo-tagged street art images from around the world. Launched iOS apps, data labeling games, public data-feeds, and web applications for search/browsing/sharing images.}
    \resumeSubItem{Remind to read}
      {An embed tool for digital publishers to send readers email reminders to finish reading long content.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Soka University of America}{Aliso Viejo, CA}
      {Bachelor of Arts, concetrating in Humanities}{Class of 2007}
    \resumeSubheading
      {Saddleback college}{Mission Viejo, CA}
      {Computer science}{2011}
    \resumeSubheading
      {Shanghai University}{Shanghai, China}
      {Chinese literature}{2012}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
